fuzzy-matching.Rmd

### 2019-02-26 notebook/algae.Rmd
WIP

```{r}
taxadb::td_create("all") # only needed once.
algae <- read_csv("~/projects/algae-names/algae_uncleanednames_NAdropped.csv")
```

@@

```{r}
length(unmatched2)
head(unmatched2, 10)

ott <- taxa_tbl("ott") %>% collect()
ott_mash <- ott %>% mutate(input = clean_names(scientificName))
```

>>>>

```{r}
taxadb::td_create("all") # only needed once.
```

```{r}
algae <- read_csv("~/projects/algae-names/algae_uncleanednames_NAdropped.csv")
```

@@

```{r}
length(unmatched2)
head(unmatched2, 10)
```

Working from the names directly:

```{r}

df <- db_mutate(r_fn = clean_names,
          tbl = "ott",
          db = td_connect(),
          col = "scientificName",
          new_column = "input")

```

```{r}
sp <- tibble(input = unmatched2)

match_binomial <- right_join(df, sp, copy=TRUE, by = "input") 
match_binomial %>% filter(!is.na(acceptedNameUsageID))
```
